Supplementary Information

### 2020-11-08 writing/transect_supplement.Rmd
fix some figures in supplement

(ref:read-compare) by ASV (**a**) and 97% OTU (**b**). ASVs/OTUs which were detected by one sequencing strategy but not the other are plotted as tick marks along the axes. Dashed line represents a constant ratio of read numbers. The blue line is a LOESS smooth of the data, with associated uncertainty in grey shading. $R^2$ value displayed is for log-transformed non-zero read numbers.

```{r read-compare-asv, fig.cap="(ref:read-compare-asv). ASVs (ref:read-compare)", fig.scap="(ref:read-compare-asv)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "ASV"
  )
```

@@

```{r read-compare-otu, fig.cap="(ref:read-compare-otu). OTUs (ref:read-compare)", fig.scap="(ref:read-compare-otu)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "OTU"
  )
```

>>>>

(ref:read-compare) which were detected by one sequencing strategy but not the other are plotted as tick marks along the axes. Dashed line represents a constant ratio of read numbers. The blue line is a LOESS smooth of the data, with associated uncertainty in grey shading. $R^2$ value displayed is for log-transformed non-zero read numbers.

```{r read-compare-asv, fig.cap="(ref:read-compare-asv). ASVs (ref:read-compare)", fig.scap="(ref:read-compare-asv)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
grid::grid.newpage()
grid::grid.draw(
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "ASV"
  )
)
```

@@

```{r read-compare-otu, fig.cap="(ref:read-compare-otu). OTUs (ref:read-compare)", fig.scap="(ref:read-compare-otu)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
grid::grid.newpage()
grid::grid.draw(
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "OTU"
  )
)
```
